---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# curtisquadata

<!-- badges: start -->
[![Lifecycle: maturing](https://img.shields.io/badge/lifecycle-maturing-blue.svg)](https://www.tidyverse.org/lifecycle/#maturing)
[![R build status](https://github.com/poissonconsulting/curtisquadata/workflows/R-CMD-check/badge.svg)](https://github.com/poissonconsulting/curtisquadata/actions)
[![Codecov test coverage](https://codecov.io/gh/poissonconsulting/curtisquadata/branch/master/graph/badge.svg)](https://codecov.io/gh/poissonconsulting/curtisquadata?branch=master)
[![License: CC0](https://img.shields.io/badge/License-CC0-green.svg)](https://creativecommons.org/publicdomain/zero/1.0/legalcode)
[![CRAN status](https://www.r-pkg.org/badges/version/curtisquadata)](https://CRAN.R-project.org/package=curtisquadata)
<!-- badges: end -->


`curtisquadata` is an R package of xx relational tibbles from the Curtis and Qua Creeks Productivity study.

```{r, message=FALSE, echo=FALSE}
library(curtisquadata)
```

```{r}
ls("package:curtisquadata") # the six tibbles
```

```{r}
#library(tibble) # for prettier printing
#capture
```

```{r}
#recapture
```

## Installation

<!-- To install the latest release from [CRAN](https://cran.r-project.org) -->
```{r, eval=FALSE, echo=FALSE}
install.packages("curtisquadata")
```

To install the developmental version from [GitHub](https://github.com/poissonconsulting/curtisquadata)
```{r, eval=FALSE}
# install.packages("remotes")
remotes::install_github("poissonconsulting/curtisquadata")
```

## Information

The study which ran from xx to xx xx. 

## Contribution

Please report any [issues](https://github.com/poissonconsulting/pkgtemplate/issues).

[Pull requests](https://github.com/poissonconsulting/pkgtemplate/pulls) are always welcome.

## Code of Conduct

Please note that the curtisquadata project is released with a [Contributor Code of Conduct](https://contributor-covenant.org/version/2/0/CODE_OF_CONDUCT.html).
By contributing to this project, you agree to abide by its terms.

## Acknowledgements

