---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# curtisquadata

<!-- badges: start -->
[![Lifecycle: stable](https://img.shields.io/badge/lifecycle-stable-brightgreen.svg)](https://lifecycle.r-lib.org/articles/stages.html#stable)
[![R build status](https://github.com/poissonconsulting/curtisquadata/workflows/R-CMD-check/badge.svg)](https://github.com/poissonconsulting/curtisquadata/actions)
[![Codecov test coverage](https://codecov.io/gh/poissonconsulting/curtisquadata/branch/master/graph/badge.svg)](https://codecov.io/gh/poissonconsulting/curtisquadata?branch=master)
[![License: CC0](https://img.shields.io/badge/License-CC0-green.svg)](https://creativecommons.org/publicdomain/zero/1.0/legalcode)
[![CRAN status](https://www.r-pkg.org/badges/version/curtisquadata)](https://CRAN.R-project.org/package=curtisquadata)
<!-- badges: end -->

`curtisquadata` is an R package of 15 relational tibbles from the Curtis and Qua Creeks Productivity study.

```{r, message=FALSE, echo=FALSE}
library(curtisquadata)
```

```{r}
ls("package:curtisquadata") # the tibbles
```

```{r}
library(tibble) # for prettier printing
efvisit
```

```{r}
effish
```

## Installation

<!-- To install the latest release from [CRAN](https://cran.r-project.org) -->
```{r, eval=FALSE, echo=FALSE}
install.packages("curtisquadata")
```

To install the developmental version from [GitHub](https://github.com/poissonconsulting/curtisquadata)
```{r, eval=FALSE}
# install.packages("remotes")
remotes::install_github("poissonconsulting/curtisquadata")
```

## Information

The study which ran from 2015 to 2017 collected data on the water quality and temperature, periphyton, 
benthic invertebrates and fish populations of Curtis and Qua Creeks in the Salmo Watershed, British Columbia.

The final report by [Nellestijn and Irvine (2017)](http://a100.gov.bc.ca/appsdata/acat/documents/r52848/COL_F17_F_1410_1507656727296_7649412937.pdf) assesses whether the creeks are suitable for nutrient restoration.

The data are analysed by [Thorley and Dalgarno (2018)](https://www.poissonconsulting.ca/analyses/curtis-qua-prod-17/)

## Contribution

Please report any [issues](https://github.com/poissonconsulting/pkgtemplate/issues).

[Pull requests](https://github.com/poissonconsulting/pkgtemplate/pulls) are always welcome.

## Code of Conduct

Please note that the curtisquadata project is released with a [Contributor Code of Conduct](https://contributor-covenant.org/version/2/0/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.


## Acknowledgements

The study was primarily funded by the Fish and Wildlife Compensation Program 
and partially funded by the Salmo Watershed Streamkeepers Society.
Lynn Westcott of Westcott Environmental Services identified and counted the benthic macroinvertebrates.
CARO Analytic analysed the water and periphyton samples
